PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-02-02 paper/ms.tex
gully edits to the manuscript, addition of .bib file and a few references

        \texttt{LightCurve} object provides methods described in
        Table~(\ref{tab:methods})

@@

\section{Target Pixel File Basics}
    \subsection{The \texttt{KeplerTargetPixelFile} class}
        A \texttt{KeplerTargetPixelFile} object can be instantiated
        by passing a \texttt{path} (URL or local) of a target pixel file.
        Optionally, the user the select to throw away frames that contain
        a specific flag by using the \texttt{quality\_bitmask} argument.

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{}
\begin{verbatim}
import numpy as np
from pyke import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

@@

Cotrending basis vectors (CBVs) correction consists in removing global correlated
systematics that occurs in a given channel [add reference]. The procedure of
designing the CBVs is discussed in [add reference].

Briefly, given a set of $n$ CBVs, one is interested in finding a set of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

@@

Then, the cbv-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

In this setting, the user is left to choose the cost function and the number
of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].

The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}).

@@

In the same fashion, we can apply cotrending basis vector correction to
$\mathcal{K}\mathit{2}$ lightcurves.

For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
The selection of the number of CBVs is also done empirically by inspecting the
grid search curve.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

@@

A runnable code to perform PSF photometry in \texttt{EPIC 246199087}
(Trappist-1), can be written as follows:

@@

The photometric results are stored in the $c \times 4$ matrix, where $c$ is the
number of frames (cadences).

@@

\subsection{Motion-dependent Correlated Noise}
\label{subsection:motion}

@@

>>>>

        The \texttt{LightCurve} object provides methods described in
        Table~(\ref{tab:methods}).

@@

\section{Target Pixel File Basics}
    \subsection{The \texttt{KeplerTargetPixelFile} class}
        A \texttt{KeplerTargetPixelFile} object can be instantiated
        by passing a \texttt{path} (URL or local) of a target pixel file.
        Optionally, the user can elect to throw away frames that contain
        a specific flag by using the \texttt{quality\_bitmask} argument.

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}
\begin{verbatim}
import numpy as np
from pyke import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

@@

Cotrending basis vectors (CBVs) can remove global correlated
systematics present in a given channel \cite{2012PASP..124.1000S}.

Given a set of $n$ CBVs, one is interested in finding a set of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

@@

Then, the CBV-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

An example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

Fig~\ref{fig:cbv-correction} illustrates the CBV correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

In this setting, the user is left to choose the cost function and the number
of CBVs. Experimentation showed that $p=1$ yields robust (non-overfitted)
results; $p=1$ defines the outlier-resilient $\ell_1$-norm
\cite{2014sdmm.book.....I}.

Improperly tuning the number of CBVs can cause over-/under-fitting. One
way to identify a reasonable number of CBVs is to perform a grid search
as shown in Fig~(\ref{fig:cbv-grid-search}).

@@

We can similarly apply cotrending basis vector correction to
 lightcurves.

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{2014sdmm.book.....I}.

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

@@

The example below illustrates PSF photometry on the target \texttt{EPIC 246199087}
(Trappist-1):

@@

The photometric results are stored in a $c \times 4$ matrix, where $c$ is the
number of frames (cadences).

@@

\subsection{Motion-dependent Correlated Noise}

Spacecraft-induced correlated noise remains one of the greatest hurdles to analyzing K2 lightcurves.  Many algorithms have been developed to mitigate motion-dependent artifacts \cite{vanderburg14}.  Local and global Gaussian Process covariance kernels...

\label{subsection:motion}

@@

\clearpage

%% MGS 2/2018: Uncomment below to enable references.
%\bibliographystyle{aasjournal}
%\bibliography{ms}
